data_cleaning_longer_period

### 2024-09-06 code/manuscript_data_cleaning.Rmd
new figures
getting right time period
new addons

@@

fins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
names(fins.revenue.expenses) <- gsub("^X\\.", "", names(fins.revenue.expenses))
names(fins.revenue.expenses) <- gsub("\\.\\.", "", names(fins.revenue.expenses))

@@

 included.years <- 2014:2023
 included.treat <- 2016:2023

>>>>

## Total Patients served by Year
```{r}
read.csv(file = "//Users/markow/Dropbox/Git/APMs/data_processed/Merged_Table3B.csv") %>% 
  select(Year, T3B_L4_CA) %>% 
  group_by(Year) %>% 
  summarise(sum(T3B_L4_CA, na.rm = TRUE))

@@

fins.revenue.expenses <- read.csv("//Users/markow/Dropbox/Git/Data/FQHC_Revenue_vs_Expenses.csv", header = TRUE)
table(fins.revenue.expenses$X.form_year..)
names(fins.revenue.expenses) <- gsub("^X\\.", "", names(fins.revenue.expenses))
names(fins.revenue.expenses) <- gsub("\\.\\.", "", names(fins.revenue.expenses))

@@

included.years <- 2010:2021
included.treat <- 2013:2019
